Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2018-02-22 manuscript/manuscript.tex

From equation \ref{eq:glq-var-dens} we saw that the GLQ approximates the volume integrals as the gravitational effect of point masses located at the nodes of the quadrature.
If we set the GLQ orders to fixed values, it's easy to conclude that the nearer the computation point is to the tesseroid, the accuracy of the approximation is reduced and the point masses effect becomes more noticeable than the tesseroid we want to approximate.
A more complete analysis of this conclusion can be found in \citet{Ku1977, Li2011, Uieda2016}.

@@

\noindent where $i \in \{\lambda, \phi, r\}$, $d$ is the distance between the geometric centre of the tesseroid and the computation point, and $D$ is a predefined value called distance-size ratio.
If the inequality \ref{eq:distance-size-ratio} is not held for at least one spherical coordinate, then the tesseroid must be divided by half in that direction.
A more complete description of the modified adaptive discretization algorithm can be found in \citet{Uieda2016}.
On the contrary, if the inequality is satisfied for every spherical coordinate, the algorithm computes the desired gravity field using the GLQ approximation.

>>>>

From equation \ref{eq:glq-var-dens} we saw that the GLQ approximates the volume integrals as the gravitational effect of point masses located at the nodes of the quadrature.
If we set the GLQ orders to fixed values, it's easy to conclude that the nearer the computation point is to the tesseroid, the accuracy of the approximation is reduced and the point masses effect becomes more noticeable than the tesseroid we want to approximate.
A complete analysis of this conclusion can be found in \citet{Ku1977, Li2011, Uieda2016}.

@@

\noindent where $i \in \{\lambda, \phi, r\}$, $d$ is the distance between the geometric centre of the tesseroid and the computation point, and $D$ is a predefined value called distance-size ratio.
If the inequality \ref{eq:distance-size-ratio} is not held for at least one spherical coordinate, then the tesseroid must be divided by half in that direction.
A complete description of the modified adaptive discretization algorithm can be found in \citet{Uieda2016}.
On the contrary, if the inequality is satisfied for every spherical coordinate, the algorithm computes the desired gravity field using the GLQ approximation.
